---
title: "IDD comments"
output:
  html_document: default
---

```{r setup, include=FALSE}

library(pins)
library(tidyverse)
library(knitr)

knitr::opts_chunk$set(echo = FALSE)

board_register_rsconnect("SPACED",
                         server = "https://involve.nottshc.nhs.uk/rsconnect",
                         key = Sys.getenv("CONNECT_API_KEY"))

df <- pin_get("chrisbeeley/trustData", board = "SPACED")

# filter by team

team_codes <- c(409L, 601L, 602L, 603L, 605L, 607L, 608L, 610L, 612L, 613L, 
                615L, 616L, 617L, 618L, 619L, 512L, 800L, 801L, 802L, 803L, 
                31609L, 31540L)

df_filter <- df %>% 
  filter(TeamC %in% team_codes,
         Date > "2019-07-01", Date < "2020-07-01")

```

## Report spec

All IDD services, irrespective of division/directorate (so, specialist IDD dental in CS division, IDD directorate in Rampton, IDD services like Orion and Horizon Unit in MH and CAMHS IDD in MH). Jul 2019 - Jun 2020

Any feedback comments you can find mentioning keywords accessing any other services 

Keywords: IDD, ASD, Autistic Spectrum Disorder, Autism, Autistic, Learning Disability, Learning  Difficulties, Down Syndrome, Down's syndrome

Main themes from feedback in each service and then aggregated if a pattern is emerging spanning multiple teams/divisions.

Quotes which illustrate the theme would be great, just a handful across the whole report

## What could we improve?

```{r, results = "asis"}

for(i in unique(df_filter$Location)){
  
  cat(paste0("<h3>", i, "</h3>"))
  
  df_filter %>%
    filter(Location == i,
           !is.na(Improve)) %>% 
    pull(Improve) %>% 
    cat(paste0("<p>", "</p>"))
  
}

```

## What did we do well?

```{r, results = "asis"}

for(i in unique(df_filter$Location)){
  
  cat(paste0("<h3>", i, "</h3>"))
  
  df_filter %>%
    filter(Location == i,
           !is.na(Improve)) %>% 
    pull(Best) %>% 
    cat(paste0("<p>", "</p>"))
  
}

```

## Search everywhere for comments

### What could we improve?

```{r}

search_string <- c(" IDD |ASD|Autistic Spectrum Disorder|Autism|Autistic|Learning Disability|Learning 
                   Difficulties|Down Syndrome|Down's syndrome")

df %>% 
  filter(Date > "2019-07-01", 
         Date < "2020-07-01",
         grepl(search_string, Improve, ignore.case = TRUE)) %>% 
  select(Improve, Location) %>% 
  kable()

```

### What did we do well?

```{r}

df %>% 
  filter(Date > "2019-07-01", 
         Date < "2020-07-01",
         grepl(search_string, Best, ignore.case = TRUE)) %>% 
  select(Best, Location) %>% 
  kable()

```


